SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-25 paper.tex
minor changes

One promising approach to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge, however, of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding verification conditions to be valid~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those must be inductive so that verifiers can automatically prove program correctness.

@@

%--------------------------------------
\subsection{Incorporating System Knowledge to Automated Verification Procedures}
%--------------------------------------

It is worth noticing that, currently, SMT-based BMC approaches check code properties in real programs, which basically address programing-language issues and general correctness, without taking into account target applications or system behavior. Such a statement is important, since, as already mentioned, many system features are being moved to software domain, which then claims for schemes that not only check if the source code is correctly written, but also if it will properly respond in real environments or under external problems. For instance, the anti-lock braking system software of a vehicle model can be bug free, but it may not work correctly if a sensor is damaged.

>>>>

One promising approach to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge, however, of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding verification conditions to be valid, {\it i.e.}, induction cannot determine the invariance of a non-inductive assertion~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those must be inductive so that verifiers can automatically prove program correctness.

@@

%--------------------------------------
\subsection{Incorporating System Model to Automated Verification Procedures}
%--------------------------------------

It is worth noticing that, currently, SMT-based BMC approaches check code properties in real programs, which basically address programing-language issues and general correctness, without taking into account target applications or system behavior. Such a statement is important, since, as already mentioned, many system features are being moved to software domain, which then requires schemes that they not only check if the source code is correctly written, but also if it will properly respond in real environments or under external problems. For instance, the anti-lock braking system software of a vehicle model can be bug free, but it may not work correctly if a sensor is damaged.
